Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-16 manuscript/manuscript.Rmd
started results section

More specifically, for each parametric noise strength $\sigma_{\text{param.}}$ choice in $[0.04, 0.08, \dots, 0.2]$, we executed the following procedure:
Sample 100 choices of perturbed parameter values, where the perturbation is as follows---each parameter $P$ is perturbed to $(1+g_P)P$ where $g_P$ is a Gaussian random variable with variance $\sigma_{\text{param.}}^2$.
For each of these parameter choices, tune the constant escapement strategy and train the DRL model on the corresponding model.
Measure the average reward difference between strategies for each of these parameter choice samples.
Average this difference over the 100 samples.
The stability results are displayed in Fig. \textbf{TBD}.

@@

We evaluated each of the three control approaches (MSY constant mortality, 80% MSY constant mortality and DRL) by running 50 episodes using the respective control rule.
In Fig. \ref{fig:timeseries} we show the time series of one such repetition.
The left panel uses an MSY constant mortality control $M^*X$, the middle panel uses $0.8 M^* X$, while the right panel is controlled by the trained DRL agent.
We see that that optimal constant mortality control leads to a near-extinction event at around $t=150$.
The constant mortality policy at $0.8 M^*$ is already conservative enough to support a sustainable path.
There, the population levels are maintained roughly in a stationary state.
Finally, the DRL time series shows an oscillatory behavior, with a slight dephase between the $Y$ and $Z$ curves, while the $X$ oscillations are roughly anticorrelated with $Z$.

>>>>

More specifically, for each parametric noise strength $\sigma_{\text{param.}}$ choice in $[0.04, 0.08, \dots, 0.2]$, we executed the following procedure:
Sample 100 choices of perturbed parameter values, where the perturbation is as follows---each parameter $P$ is perturbed to $(1+g_P)P$ where $g_P$ is a Gaussian random variable with variance $\sigma_{\text{param.}}^2$.
For each of these parameter choices, tune the constant escapement strategy and train the DRL model on the corresponding model.
Measure the average reward difference between strategies for each of these parameter choice samples using 100 replicate evaluation episodes.
Take the mean of this average difference over the 100 perturbed parameter samples.
The stability results are displayed in Fig. \textbf{TBD}.

@@

We evaluated each of the four control approaches considered -- MSY constant mortality, optimal constant escapement, PPO, and Gaussian process interpolation of the latter -- on each of the four scenarios examined (see Sec. TBD).
Furthermore, we characterized the trade-off between economic output and sustainability faced by constant mortality policies.
This was done by evaluating constant mortality policies with a fraction of the optimal mortality rate (specifically, 80%, 90% and 95%).
All evaluations were based on 100 replicate episodes for each

We will visualize the results concerning the last scenario considered (‘‘3 species, 2 of which harvested, and a time-varying parameter’’) in this section, leaving the other cases for the appendix.
This is the most complex scenario considered and where our results show the most compelling advantage of DRL methods with respect to classical strategies.

Our main result is summarized in Fig. **TBD** which displays the total reward distributions for the policy obtained through each strategy.
Here we note two surprising things:
First, optimal constant escapement performs considerably worse than not only DRL-based methods, but also than MSY.
This conceptually shows how one-dimensional intuitions on ecological control may loose validity for complex ecosystems. **(this might be unwelcome by the reviewers if not discussed properly)**
Second, we see that classical strategies have relatively spread out reward distributions as compared to DRL methods.

## Old results (to be copy-pasted above)

In Fig. \ref{fig:timeseries} we show the time series of one such repetition.
The left panel uses an MSY constant mortality control $M^*X$, the middle panel uses $0.8 M^* X$, while the right panel is controlled by the trained DRL agent.
We see that that optimal constant mortality control leads to a near-extinction event at around $t=150$.
The constant mortality policy at $0.8 M^*$ is already conservative enough to support a sustainable path.
There, the population levels are maintained roughly in a stationary state.
Finally, the DRL time series shows an oscillatory behavior, with a slight dephase between the $Y$ and $Z$ curves, while the $X$ oscillations are roughly anticorrelated with $Z$.
